---
title: "ETX5551 Assignment 3"
author: "Brayan Diaz Perez"
date: "2025-05-06"
quarto-required: ">=1.6.0"
format:
    unilur-html+solution:
        output-file: assign03-Brayan.html
        css: "assignment.css"
        embed-resources: true
unilur-solution: true
---

```{r echo=FALSE, message=FALSE}
source("setup.R")
```

**As per [Monash's integrity rules](https://www.monash.edu/student-academic-success/learnhq/maintain-academic-integrity) this assignment needs to be completed independently and not shared beyond this class.**


## 🔑 Instructions

- This is an open book assignment, and you are allowed to use any resources that you find helpful. However, **every resource used needs to be appropriately cited.** You can add the citations to the end of the report, the particular style is not important. Lack of citation of resources will incur up to **50% reduction** in final score.
- You are encouraged to use Generative AI, so that you become accustomed to where it is helpful and where it is problematic on topics related to visualisation for machine learning. You are expected to include a link to the full script(s) of your conversion at the end of your report.
- This is an exercise in conducting reproducible analyses/research. You need to turn in multiple files, compiled into one **zip** file, to be emailed to dicook@monash.edu:
    - quarto (`.qmd`)
    - `html`
    - additional supporting files such as `assignment.css`, `setup.R`, and any data files. 
It is expected that the rendering the `qmd` will produce the `html` file submitted. If the `qmd` file does not render, then the score for assignment will be **reduced by 25%**. (If your final file size is too large for email, we can use a shared drive.)
- R code should be folded so that it can be examined if interested but otherwise is hidden in the final report.
- You will use this `.qmd` file for writing your answers in the `unilur` blocks. You will need to install the `unilur` extension to get the formatting of your solutions done correctly. Follow the instructions at https://github.com/ginolhac/unilur, which says in the Terminal window of your RStudio GUI, type `quarto add ginolhac/unilur`.
- This assignment is worth 40$\times \frac{1}{3}$% of your overall score for the unit.
- **DUE DATE:** 4:30pm Friday May 30, 2025

## Exercises

#### 1.  Chapter 1, question 3, data sets `c1` and `c3`


::: unilur-solution

Write your solution here

:::

#### 2. Chapter 1, question 4a

::: unilur-solution

Write your solution here

:::

#### 3. Chapter 2, questions 1-4, using `set.seed(1257)`.

::: unilur-solution

Write your solution here

```{r}
#| code-fold: true
set.seed(1257)
```

:::

#### 3. Chapter 3, question 4, `c1` and `c3`

::: unilur-solution

Write your solution here

:::

#### 4. Chapter 4, question 4, `anomaly2`

::: unilur-solution

Write your solution here

:::

#### 5. Chapter 5, question 4

::: unilur-solution

Write your solution here

:::

#### 6. Chapter 6, question 3 `c1` and `c3`

::: unilur-solution

Write your solution here

:::

#### 7. Chapter 8, question 6

::: unilur-solution

Write your solution here

:::

#### 8. Chapter 12, project 1-7

::: unilur-solution

Write your solution here

:::


#### 9. Chapter 13, question 2

::: unilur-solution

Write your solution here

:::

#### 10. Chapter 16, question 1, 2, 3

::: unilur-solution

Write your solution here

:::

#### References

H. Wickham. ggplot2: Elegant Graphics for Data Analysis.
  Springer-Verlag New York, 2016

#### GAI Use
